Tables/Graphs for Article

### 2018-01-09 article/draft1.Rnw
proofread + revisions

model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + 
                   contain_unanswered + contain_answered + title_questionmark + 
                   text_contain_punct + text_all_lower + update + prior_effort + day +
                   sqrt(avg_tag_score) + rms::rcs(sqrt(avg_tag_length), 4) + rms::rcs(log10(text_length), 5) +
                   rms::rcs(sqrt(device_length), 5) + rms::rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
@

\section*{Abstract}

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced knowledge. Thousands of questions and answers are posted by users everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.55, 95\% CI = (2.32, 2.80))), factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.88, 95\% CI = (8.20, 9.34))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

Community-driven online question and answer forums (CQA) are becoming widely-used sources of information. These online platforms feature thousands of user-posted questions and answers and can receive millions of visits every month. The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to save money and reduce electronic waste. This company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.

As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users. This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered phone screens and faulty air conditioners, with over 100,000 solutions. As thousands of users rely on this forum for information, it is important that users receive timely answers. Fast response times enhance user experience and thus increase web traffic, which is valuable to the reputation and longevity of iFixit's \textit{Answers} forum. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how the forum design can be improved.

However, analysis and prediction of response times on CQAs has not been thoroughly investigated. There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality. This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the survival probability of a question.

@@

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions on \textit{Stack Overflow}, and created a model to predict how long a question would remain unanswered. However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions. \cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). \cite{H.fu} instead found that non-textual features, like revision and comment count on an answer or the number of points a user has, were the most useful indicators of answer quality. A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}. \cite{Anderson} took analysis further and presented models to predict the long term value of questions as well as the answers it receives. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors indicating that a question is of high quality, can also lead to faster response times. (fix this section)

@@

% Table of categorical predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Device category the question pertains to. Categories include: Android\/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
  If the question was posted on the weekend or on a weekday \\ \hline
  Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
  Whether or not the question's text is in all lower case \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See Appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See Appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title ends in a question mark \\ \hline
  Whether or not the user edited or added information to the question's text sometime after posting it. \\ \hline
  Whether or not the user made an effort to solve the problem prior to asking the question. \\ \hline
\end{tabular}
\caption{Categorical variables derived}
\label{table:categorical}
\end{table}

% Table of quantitative predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Average number of characters in each question's tags\\ \hline
  Average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a score of 0. \\ \hline
  Number of characters in the question's text \\ \hline
  Number of characters in the user-defined device name \\ \hline
  Ratio of the number of line breaks to the number of characters in the question's text \\ \hline
\end{tabular}
\caption{Continuous variables derived}
\label{table:continuous}
\end{table}

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (the date the data was downloaded). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received. Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}. See Appendix for more details on variable derivation.

@@

In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Signficant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $chi^2$ distribution \cite{find}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

@@

To obtain predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package. This function uses the Cox model and a vector of times to compute predicted survival probabilities.

@@

% Univariate analysis results
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
  \hline
  \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
  \hline \hline
  \multirow{ 3 }{ 5cm }{ Average frequency score of a question's tags }
  & Untransformed & 1.270620e-08 \\
  & Log + 1 & 1.186521e-08 \\
  & \textbf{*}Square root & 1.464184e-11 \\ \hline
  \multirow{ 3 }{ 5cm }{ Average number of characters in each question's tags }
  & Untransformed & 2.611529e-02 \\ 
  & \textbf{*}Log + 1 & 6.018542e-05 \\
  & Square root & 2.999917e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Number of characters in a question's text }
  & Untransformed & 6.947221e-12 \\
  & \textbf{*}Log & 0.000000e+00 \\
  & Square root & 1.110223e-16 \\ \hline
  \multirow{ 3 }{ 5cm }{ Number of characters in the user-defined device title }
  & Untransformed & 6.530431e-03 \\
  & \textbf{*}Log + 1 & 1.912977e-05 \\
  & Square root & 2.291424e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Ratio of the number of line breaks to the number of characters in a question's text } 
  & Untransformed & 1.398819e-07 \\
  & Log + 1 & 1.092952e-07 \\
  & \textbf{*}Square root & 1.148792e-11 \\ \hline \hline
  \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
  \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
  \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
  \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
\end{tabular}
\caption{Univariate analysis results} 
\label{table:univariate_results}
\end{table}

@@

% Splines
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{5cm} | l | l |}
  \hline
  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
  \hline
  \multirow{ 4 }{ 5cm }{ Log transformation of the number of characters in a question's text } 
  & 0 & 65862.83 \\ 
  & \textbf{*}5 & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text }
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & \textbf{*}3 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average frequency ``score'' of a question's tags }
  & \textbf{*}0 & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of the number of characters in the user-defined device title + 1 }
  & 0 & 65918.06 \\ 
  & \textbf{*}5 & 65847.34 \\ 
  & 4 & 65880.89 \\ 
  & 3 & 65898.00 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of the average number of characters in a question's tags + 1 }
  & 0 & 65920.24 \\ 
  & 5 & 65911.20 \\ 
  & \textbf{*}4 & 65910.81 \\ 
  & 3 & 65914.98 \\ 
   \hline
\end{tabular}
\caption{Determining the optimal k number of splines for each predictor} 
\label{table:splines}
\end{table}

Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Values of knots marked with an asterisk (*) were included in the final model.

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.027030 & 937.3877 & 0.0000 & 0.1401511 & 0.2683734 & 0.6341867 \\ 
  \textbf{Test Sets} & 1.986844 & 220.8309 & 0.0000 & 0.1400518 & 0.2582790 & 0.6291395 \\
  \textbf{Full Data} & 2.028512 & 1165.441 & 0.0000 & 0.1394545 & 0.2675286 & 0.6337643 \\ 
   \hline
\end{tabular}
\caption{Performance Metrics} 
\label{table:cv}
\end{table}

Average performance metrics for test and training sets and in Table \ref{table:cv}. Partial likelihood ratio statistics and p-values indicate that the model as a whole is signficantly associated with response time. However, its $R^2$ statistic and discrimination indexes are considerably low. Metrics did not change significantly from training to test sets, indicating that the model was not overfit. Metrics for the final model's performance on the full data, also found in Table \ref{table:cv}, are consistent with metrics found in cross-validation and indicate low predictive accuracy.

>>>>

model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + 
                    contain_unanswered + contain_answered + title_questionmark + 
                    text_contain_punct + text_all_lower + update + prior_effort + 
                    day + sqrt(avg_tag_score) + rms::rcs(log10(text_length), 5) + 
                    rms::rcs(log10(avg_tag_length + 1), 4) + rms::rcs(log10(device_length + 1), 5) + 
                    rms::rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
@

\section*{Abstract} % fix the hazard ratios!!!!

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR...), factors related to the question's title (e.g., whether or not it was phrased as a question (HR..)), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR..)). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

Community-driven online question and answer forums are becoming widely-used sources of information. These online platforms feature thousands of user-posted questions and answers and can receive millions of visits every month. The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to save money and reduce electronic waste. This company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.

As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users. This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered phone screens and faulty air conditioners, with over 100,000 user-posted solutions. As thousands of users rely on this forum for information, it is important that users receive timely answers. Fast response times have been shown to be associated with user satisfaction and in turn increase web traffic, which is valuable to the reputation and longevity of the CQA \cite{Rechavi2011}. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask questions to minimize response times and for how the forum design can be improved.

However, analysis and prediction of response times on CQAs has not been thoroughly investigated. There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality. This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to response time and to predict the survival probability of a question.

@@

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions and created a model to predict how long a question would remain unanswered. All research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions. \cite{Blumenstock} also determined that textual features, e.g. word count, was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). \cite{H.fu} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality. A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.

@@

% Table of categorical predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
  If the question was posted on a weekend or on a weekday \\ \hline
  Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
  Whether or not the question's text is in all lower case \\ \hline
  Whether or not the question's title contains at least one word considered to be ``frequently used'' among answered questions \\ \hline
  Whether or not the question's title contains at least one word considered to be ``frequently used'' among unanswered question \\ \hline
  Whether or not the question's title ends in a question mark \\ \hline
  Whether or not the user edited or added information to the question's text after posting it \\ \hline
  Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
\end{tabular}
\caption{Categorical variables derived}
\label{table:categorical}
\end{table}

% Table of quantitative predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Average number of characters in each question's tags (Average tag length) \\ \hline
  Average frequency for all of a question's tags. Frequency defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a value of 0 (Average tag frequency) \\ \hline
  Number of characters in the question's text (Text length) \\ \hline
  Number of characters in the user-defined device name (Device name length) \\ \hline
  Ratio of the number of line breaks to the number of characters in the question's text (Line break to text length ratio) \\ \hline
\end{tabular}
\caption{Continuous variables derived}
\label{table:continuous}
\end{table}

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (the date the data was downloaded). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received. See Appendix for examples of answered and unanswered questions. Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}. See Appendix for more details on variable derivation.

@@

In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Signficant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $chi^2$ distribution \cite{find}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

@@

To obtain predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package in R. This function uses the Cox model and a vector of times to compute predicted survival probabilities.

@@

% Univariate analysis results
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
  \hline
  \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
  \hline \hline
  \multirow{ 3 }{ 5cm }{ Average tag frequency }
  & Untransformed & 1.270620e-08 \\
  & Log + 1 & 1.186521e-08 \\
  & \textbf{*}Square root & 1.464184e-11 \\ \hline
  \multirow{ 3 }{ 5cm }{ Average tag length }
  & Untransformed & 2.611529e-02 \\ 
  & \textbf{*}Log + 1 & 6.018542e-05 \\
  & Square root & 2.999917e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Device name length }
  & Untransformed & 6.530431e-03 \\
  & \textbf{*}Log + 1 & 1.912977e-05 \\
  & Square root & 2.291424e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
  & Untransformed & 1.398819e-07 \\
  & Log + 1 & 1.092952e-07 \\
  & \textbf{*}Square root & 1.148792e-11 \\ 
  \multirow{ 3 }{ 5cm }{ Text length }
  & Untransformed & 6.947221e-12 \\
  & \textbf{*}Log & 0.000000e+00 \\
  & Square root & 1.110223e-16 \\ \hline \hline
  \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
  \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
  \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
  \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
\end{tabular}
\caption{Univariate analysis results} 
\label{table:univariate_results}
\end{table}

@@

% Splines
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{5cm} | l | l |}
  \hline
  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
  \hline
  \multirow{ 4 }{ 5cm }{ Log transformation of text length } 
  & 0 & 65862.83 \\ 
  & \textbf{*}5 & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of line breaks to text length ratio }
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & \textbf{*}3 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average tag frequency }
  & \textbf{*}0 & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of device name length + 1 }
  & 0 & 65918.06 \\ 
  & \textbf{*}5 & 65847.34 \\ 
  & 4 & 65880.89 \\ 
  & 3 & 65898.00 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of average tag length + 1 }
  & 0 & 65920.24 \\ 
  & 5 & 65911.20 \\ 
  & \textbf{*}4 & 65910.81 \\ 
  & 3 & 65914.98 \\ 
   \hline
\end{tabular}
\caption{Determining the optimal k number of splines for each predictor} 
\label{table:splines}
\end{table}

Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Those marked with an asterisk (*) were included in the final model.

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.027030 & 937.3877 & 0.0000 & 0.1401511 & 0.2683734 & 0.6341867 \\ 
  \textbf{Test Sets} & 1.986844 & 220.8309 & 0.0000 & 0.1400518 & 0.2582790 & 0.6291395 \\
  \textbf{Full Data} & 2.028051 & 1165.0321 & 0.0000 & 0.1394092 & 0.2672884 & 0.6336442 \\ 
   \hline
\end{tabular}
\caption{Performance Metrics} 
\label{table:cv}
\end{table}

Average performance metrics for test and training sets are in Table \ref{table:cv}. Partial likelihood ratios and p-values indicate that the model as a whole is signficantly associated with response time. However, $R^2$ statistics and discrimination indexes are considerably low. Metrics for the final model's performance on the full data, also found in Table \ref{table:cv}, are consistent with metrics found in cross-validation and indicate low predictive accuracy. Results for training, test, and the full data did not change significantly, indicating that the model was not overfit.

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{3.5cm} p{4cm}| c | l | c |}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{95\% CI} & \textbf{p-value} \\ \hline
  \multirow{ 9 }{ 3.5 cm }{ Device Category } & Apple Product & \hl{0.9346} (0.0476) & & 0.000000e+00 \\ 
  & Camera & -0.3199 (0.0476) & & \\ 
  & Electronics & -0.0138 (0.0904) & & \\ 
  & Game Console & 0.2458 (0.0784) & & \\ 
  & Home & 0.3368 (0.0697) & & \\ 
  & Other & -0.1304 (0.0555) & & \\ 
  & PC & 0.2818 (0.0597) & & \\ 
  & Tablet & -0.1566 (0.0815) & & \\ 
  & Vehicle & 0.4056 (0.0695) & & \\ 
  \hline
  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & \hl{-0.1334} (0.0331) & & 5.525114e-05 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & & 6.204270e-01 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) & & 6.065638e-03 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) & & 2.604130e-01 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & \hl{-0.2808} (0.0340) & & 1.110223e-16 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) & & 9.880985e-15 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857) & & 5.027830e-04 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364) & & 3.300423e-03 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362) & & 4.534803e-02 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Square root of the average tag frequency } & 2.2609 (0.7196) & & 1.679666e-03 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{3}{*}{Square root of average tag length} } & -0.0814 (0.0309) & & \\
  & & 0.5945 (0.2661) & & \\
  & & -1.5879 (0.7231) & & \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{4}{*}{Log of text length} } & -0.0619 (0.1856) & & \\
  & & -0.5052 (0.8452) & & \\
  & & 2.9957 (4.1706) & & \\
  & & -4.4755 (6.8975) & & \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{4}{*}{Log of device name length} } & -0.0488 (0.0714) & & \\
  & & -0.4348 (0.9724) & & \\
  & & 1.2208 (2.3149) & & \\
  & & -1.3199 (2.3255) & & \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{2}{*}{Square root of line break to text length ratio} } & -0.0076 (0.4776) & & \\
  & & 0.4345 (0.7265) & & \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model} 
\label{table:coefficients}
\end{table}

% Final model statistics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r |}
  \hline
  \textbf{LR} & 1265.291 \\ \hline
  \textbf{p-value} & 0 \\ \hline
  \textbf{$R^2$} & 0.150 \\ \hline
  \textbf{\textit{Dxy}} & 0.267 \\ \hline
\end{tabular}
\caption{Final model statistics} 
\label{table:final model}
\end{table}
